---
title: "Craigslist Personals Ads Analysis"
author: "Dan Conroy-Beam"
date: "2022-12-07"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir="../")

######Packages#######
library(qgraph)
library(igraph)
library(ggplot2)
library(reshape2)
library(plyr)
library(lmerTest)
library(maps)
library(mapproj)

```






```{r dataPrep}
######Data Preparation####

#Load the raw data
#For some reason, this list.files() workaround is the only way I can get the data to load and knit
data<-read.csv(paste0("Human Data/Processed Data/",list.files("Human Data/Processed Data/")))



#Cut out unnecessary columns
data<-data[,-c(1:2,9:10,12:14,17)]

#Rename some columns for ease of use
names(data)[c(1:12,16,37:136)]<-c("board",
                                  "country",
                                  "state","region",
                                  "language",
                                  "datetime",
                                  "gso",
                                  "images",
                                  "post",
                                  "age",
                                  "bodytype",
                                  "height",
                                  "sti",
                                  paste0("fac",1:50),
                                  paste0("fac",1:50,"_High"))


#Cut out themes that didn't have clear interpretations
data<-data[,-c(50,53,77,82,100,103,127,132)]

#Create a dataframe with the interpreted theme labels
facLabels<-data.frame("factors"=(1:50)[-c(14,17,41,46)])

#Enter the labels
facLabels$label<-c("1. Companionship",
                  "2. Explicit Sex","3. Gay Male Sex",
                  "4. Male Oral Sex","5. Dom./Sub.",
                  "6. Activities (Outings)","7. Commitment",
                  "8. Erotic Massage.","9. Female Mate Prefs.",
                  "10. Gay Anal Sex","11. Easygoing/Friendly",
                  "12. Cuckoldry/Threesome",
                  "13. Gay Body Description",
                  "15. Female Oral Sex","16. Relationship Types",
                  "18. Affair/Infidelity","19. Appearance Desc.",
                  "20. Verification/Proof",
                  "21. Crossdressing/Feet/Underwear",
                  "22. Reply Inst.","23. Rough Sex/Degradation",
                  "24. Dad & Son/Bear & Cub","25. Affection/Intimacy",
                  "26. Picture Exchange/Youth","27. General BDSM",
                  "28. Incognito Sex","29. Scheduling",
                  "30. Quickies","31. Activities (At Home)",
                  "32. Clean/Safe/Discreet","33. Female Body Desc.",
                  "34. Chill/Hangout","35. Mature Women/BBW",
                  "36. Race/Ethnicity","37. Male Sexual Prowess",
                  "38. Black/Latino Men","39. Transgender",
                  "40. Incest","42. Voyeurism/Exhibitionism",
                  "43. British Slang","44. Spanking/Discipline",
                  "45. Young/Sugar Daddy","47.Measurements/Foot Fetish",
                  "48. Married/Curious","49. Blue Collar Fantasy",
                  "50. Height/Weight/Age")

facLabels$label<-factor(facLabels$label,levels=facLabels$label)

#Make gender/sexual orientation a factor
data$gso<-as.factor(data$gso)

#Relabel missing values as NA
levels(data$gso)[1]<-"NA"

#Convert age to a numeric
data$age<-suppressWarnings(as.numeric(as.character(data$age)))

#Eliminate implausible ages
data$age[data$age>100]<-NA

#Convert height into a character temporarily
data$height<-as.character(data$height)

#Convert heights to numerics
data$height<-suppressWarnings(as.numeric(data$height))

```






# Q1: What are the demographics of Craigslist?
```{r gso}

###Gender and Sexual Orientation###

#Create a dataframe with frequencies and proportions of
#different gender and sexual orientations
gsoTable<-as.data.frame(table(data$gso))
names(gsoTable)<-c("gso","freq")

#Calculation proportions for each category
gsoTable$prop<-round(100*gsoTable$freq/sum(gsoTable$freq),2)

#Re-order factor levels according to frequency
gsoTable$gso<-factor(gsoTable$gso,
                     levels=levels(gsoTable$gso)[order(gsoTable$freq,
                                                       decreasing=T)])

#And do the same for the whole dataframe
data$gso<-factor(data$gso,
                 levels=levels(data$gso)[order(gsoTable$freq,
                                               decreasing=T)])

#Re-order the dataframe
gsoTable<-gsoTable[order(gsoTable$freq,
                         decreasing=T),]

#Plot frequencies and proportions of gender and sexual orientation
gsoPlot<-qplot(gso,prop,data=gsoTable
               ,fill=gso,geom="blank",
               xlab="Gender/Sexual Orientation",
               ylab="Proportion of All Ads")+
  geom_bar(stat="identity")+
  geom_text(aes(x=gso,y=prop,label=freq,vjust=-.5))+
  theme_grey(base_size=20)+
  theme(legend.position="none",
        axis.text.x=element_text(angle=90,vjust=.25))

```



```{r gRatios}

###Gender Ratios###

#Compute ratio of heterosexual men to heterosexual women
mwRatio<-gsoTable$freq[gsoTable$gso=="m4w"]/
  gsoTable$freq[gsoTable$gso=="w4m"]

#Compute ratio of gay men to lesbians
glRatio<-gsoTable$freq[gsoTable$gso=="m4m"]/
  gsoTable$freq[gsoTable$gso=="w4w"]

#Compute ratio of couples looking for women to couples looking for men
cplmwRatio<-gsoTable$freq[gsoTable$gso=="mw4w"]/
  gsoTable$freq[gsoTable$gso=="mw4m"]

#Compute ratio of men looking for couples to women looking for couples
mwcplRatio<-gsoTable$freq[gsoTable$gso=="m4mw"]/
  gsoTable$freq[gsoTable$gso=="w4mw"]

```



```{r marketEffects}
###Market Effects###

#Calculate how many pieces of optional information each ad provies
data$infonum<-rowSums(sapply(10:36,function(y) !(data[,y] %in% c(NA,"NA",""," "))))

#Also add in whether or not the ad included at least one image
data$infonum<-data$infonum+as.numeric(data$images>0)

#Calculate the average amount of information included as a function of GSO category
gsoInfo<-tapply(data$infonum,data$gso,mean)

#Create a dataframe to store this information
demandInfo<-data.frame("gso"=names(gsoInfo),"info"=gsoInfo)

#Calculate, for each GSO category, the ratio of people seeking that category to people posting in that category
#Higher values here indicate that this group is relatively more in demand
demandInfo$dratio<-gsotable$freq[c(1,3,2,11,6,5,7,8,16,10,4,18,22,17,15,9,14,12,21,24,19,13,25,20,23)]/gsotable$freq[c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25)]

#Also determine, for control/non-independence issues, which pairing each category belongs to
pairpos<-c(1,3,2,11,6,5,7,8,16,10,4,18,22,17,15,9,14,12,21,24,19,13,25,20,23)
demandInfo$gsopair<-as.factor(sapply(1:length(pairpos),function(x) ifelse(pairpos[pairpos[x]] %in% pairpos[1:(x-1)],pairpos[x],x)))

#Insert this information back into the full dataframe
data$dratio<-NA
data$gsopair<-NA

for(i in unique(data$gso)){
  data$dratio[data$gso==i]<-demandInfo$dratio[demandInfo$gso==i]
  data$gsopair[data$gso==i]<-demandInfo$gsopair[demandInfo$gso==i]
}

#Estimate the relationship between demand ratio and information provided
#People who belong to more in-demand groups provide less information
#This is true even if you remove outlier groups with very high demand ratios
inforeg<-lmer(infonum~dratio+(1|gsopair),data=data)
inforeg2<-lmer(infonum~dratio+(1|gsopair),data=data[data$dratio<5,])

demandInfoPlot<-qplot(dratio,infonum,data=data,color=gso,xlab="Demand Ratio (# Posts Seeking/# Posts Offering)",ylab="Pieces of Optional Information Provided",geom="blank")+
  theme_grey(base_size=15)+geom_jitter(width=.40)+scale_color_discrete(name="Gender/\nSex Orient.")+
  geom_abline(intercept=summary(inforeg)$coefficients[1,1],slope=summary(inforeg)$coefficients[2,1],lwd=1.5)

```


```{r ageHeight}

###Plots of age and height###
#I don't think these are interesting, but I'd already generated them
#so I guess I'll keep them

#Plot age across gso groups
#Limiting to m4m, m4w, w4m, w4w for now
agePlot<-qplot(gso,age,data=data[data$gso %in% 
                                   c("m4m","m4w", "w4m","w4w"),],
               fill=gso,xlab="Gender/Sexual Orientation",
               ylab="Age",
               geom="blank")+
  geom_violin()+
  geom_boxplot(width=.1)+
  theme_grey(base_size=20)+
  theme(legend.position="none",
        axis.text.x=element_text(angle=90,vjust=.25))

ageMeans<-tapply(data$age,
                 data$gso,
                 function(x) mean(x,na.rm=T))

#Plot height across gso groups
#Limiting to m4m, m4w, w4m, w4w for now
heightPlot<-qplot(gso,height,data=data[data$gso %in% 
                                         c("m4m","m4w","w4m","w4w"),],
                  fill=gso,
                  xlab="Gender/Sexual Orientation",
                  ylab="Height",geom="blank")+
  geom_violin()+
  geom_boxplot(width=.1)+
  theme_grey(base_size=20)+
  theme(legend.position="none",
        axis.text.x=element_text(angle=90,vjust=.25))
```



```{r relstat}

###Relationship status###

#Convert blanks to NA
levels(data$status)[1]<-"NA"

#Create a new variable for storing just interesting relationship statuses
data$relstat<-as.character(data$status)
data$relstat<-ifelse(data$relstat %in% 
                       c("married",
                         "NA",
                         "single",
                         "partnered",
                         "divorced",
                         "widowed",
                         "separated"),data$relstat,NA)

#Make relationship status a factor and reorder the factor levels
data$relstat<-as.factor(data$relstat)
data$relstat<-factor(data$relstat,
                     levels=levels(data$relstat)[c(3,6,4,2,1,5,7)])

#Generate a table of relationship status by gso
relstatTable<-as.data.frame(table(data$relstat,data$gso))

colnames(relstatTable)<-c("status","gso","freq")
relstatTable$prop<-100*unlist(tapply(relstatTable$freq,relstatTable$gso,function(x) x/sum(x)))



relstatPlot<-qplot(gso,prop,
                   fill=status,
                   data=relstatTable[relstatTable$status!="NA" 
                                     & relstatTable$gso %in%
                                       c("m4m","m4w","w4m","w4w"),],
                   xlab="Gender/Sex. Orient",
                   ylab="Proportion of Ads\n(by G/So)",geom="blank")+
  geom_bar(stat="identity",position="dodge")+
  theme_grey(base_size=15)+
  geom_text(data=relstatTable[relstatTable$status!="NA"
                              & relstatTable$gso %in% 
                                c("m4m","m4w","w4m","w4w"),],
            aes(label=freq,x=gso,color=status,y=prop+2),
            position=position_dodge(width=.9),fontface="bold")



#A large number of m4m are married. 
#Many of these explicitly mention being bisexual:
bicheckM4m<-mean(apply(data[data$gso=="m4m" & 
                              data$relstat=="married",],1,function(x)
                                grepl("bi",as.character(x[9]),
                                      ignore.case=T)))

#Same for w4w
bicheckW4w<-mean(apply(data[data$gso=="w4w" &
                              data$relstat=="married",],1,function(x)
                                grepl("bi",as.character(x[9]),
                                      ignore.case=T)))

#But less so for m4w or w4m
bicheckM4w<-mean(apply(data[data$gso=="m4w" & 
                              data$relstat=="married",],1,function(x)
                                grepl("bi",as.character(x[9]),
                                      ignore.case=T)))
bicheckW4m<-mean(apply(data[data$gso=="w4m" & 
                              data$relstat=="married",],1,function(x)
                                grepl("bi",as.character(x[9]),
                                      ignore.case=T)))



#A large number of the w4w are also couples looking for a woman to join them
cplcheckW4w<-mean(apply(data[data$gso=="w4w" & 
                               data$relstat=="married",],1,function(x)
                                 grepl("couple|poly|watch|\\<us\\>|\\<we\\>",
                                       as.character(x[9]),
                                       ignore.case=T)))

#Less so for the other categories
cplcheckM4m<-mean(apply(data[data$gso=="m4m" & 
                               data$relstat=="married",],1,function(x)
                                 grepl("couple|poly|watch|\\<us\\>|\\<we\\>",
                                       as.character(x[9]),
                                       ignore.case=T)))
cplcheckM4w<-mean(apply(data[data$gso=="m4w" & 
                               data$relstat=="married",],1,function(x) 
                                 grepl("couple|poly|watch|\\<us\\>|\\<we\\>",
                                       as.character(x[9]),
                                       ignore.case=T)))
cplcheckW4m<-mean(apply(data[data$gso=="w4m" &
                               data$relstat=="married",],1,function(x) 
                                 grepl("couple|poly|watch|\\<us\\>|\\<we\\>",
                                       as.character(x[9]),
                                       ignore.case=T)))

```



### Q1.1: Ads come overwhelmingly from men seeking men and men seeking women
```{r gsoResults,fig.width=8}
gsoTable
gsoPlot
```



### Q1.2: Heterosexual men grealy outnumber heterosexual women and gay men greatly outnumber lesbians

Ratio of heterosexual men to heterosexual women: `r mwRatio`  
Ratio of gay men to lesbians: `r glRatio`



### Q1.3: Couples overwhelmingly seek women relative to men, but men overwhelmingly seek to join couples relative to women

Ratio of couples seeking men to seeking women: `r cplmwRatio`  
Ratio of men seeking couples to women seeking couples: `r mwcplRatio`  



### Q1.4: Most people are single, but a sizeable number are in a relationship
```{r relstatResults}
relstatPlot
```

Many of these appear to be bisexual men (`r bicheckM4m`) and women (`r bicheckW4w`) looking for same-sex partners. This is less the case for peple looking for opposite-sex partners (`r bicheckM4w`) and women (`r bicheckW4m`)

For w4w primarily, many are also couples seeking a third:  
w4w: `r cplcheckW4w`  
m4w: `r cplcheckM4w`  
w4m: `r cplcheckW4m`  
m4m: `r cplcheckM4m`  

***

# Q2: What are the themes of Craigslist?

Theme labels were generated in a multi-step process.

(1) 3 RAs independently read the factor loadings but *not* the ads  
These RAs generated independent labels for the themes  
These were adjusted to a set of consensus labels based on discussion


(2) At this point, the factor solution was adjusted slightly due to loss of the original files  
The factors remained largely the same, but some factors split
DCB re-labeled the new factors using the consensus labels

(3) Two separate RAs read the theme labels and the 100 highest scoring ads for each theme  
Based on discussion, these RAs and DCB revised the theme labels as needed.

Factors 14, 17, 41, and 46 were not easily interpretable after this process  
These are excluded from all analyses

The final labels were:  
`r facLabels`


***


# Q3: Is there a distinction between LT and ST mating?

```{r cornet}
##Correlation Network plot##

#Compute the theme correlation matrix
cormat<-cor(data[,37:82],use="pairwise.complete.obs")

#Convert to a 0-1 scale so that negative correlations are treated like low association
cormat2<-cormat
cormat2<-(cormat+1)/2

#Label
rownames(cormat2)<-faclabels$factors
colnames(cormat2)<-faclabels$factors


#Plot the correlation network
cornet<-qgraph(cormat2,graph="cor",layout="spring")

#Convert to an igraph object for analysis
g<-as.igraph(cornet)

#Detect communities in the network
clust<-cluster_optimal(g)

#Determine which themes belong to which detected communities
comms<-faclabels
comms$comm<-clust$membership

#Re-plot network with community information
cornet2<-qgraph(cormat2,
                graph="cor",
                layout="spring",
                groups=as.factor(comms$comm),
                legend=F,minimum=.5)

```



```{r kmeans}

###K-Means Clustering###

#Draw a subsample of the data for estimating k
dataSamp<-data[sample(nrow(data),nrow(data)*.10,replace=F),]

#Extract just the factors
dataSamp<-dataSamp[,37:82]

#Standardize the factor scores to minimize differences between scores
dataSamp<-apply(dataSamp,2,scale)

#Run the K-means with a variety of values of k
wss<-sapply(1:10,function(x) 
  kmeans(na.omit(dataSamp),
         x,
         algorithm="Lloyd",
         iter.max=200)$tot.withinss)

#Plot the total WSS; k = 5 seems reasonable
wssPlot<-qplot(1:10,
               wss,
               xlab="Number of Clusters",
               ylab="Total Within SS",size=I(2))

#Set a seed to make these analyses reproducible
set.seed(01052020)

#Fit the k-means
clust<-kmeans(na.omit(scale(data[,37:82])),
              5,
              algorithm="Lloyd",
              iter.max=300)

#Create a dataframe of cluster means
clustMeans<-data.frame("cluster"=as.factor(rep(1:5,times=nrow(faclabels))),
                       "factor"=rep(faclabels$label,each=5),
                       "mean"=as.vector(clust$centers))

#Plot the clusters
kMeansPlot<-qplot(factor,mean,fill=cluster,data=clustMeans,
                  geom="blank",xlab="Theme",ylab="Mean (Z-scored)")+
  geom_bar(stat="identity",position="dodge",width=.75,color="black")+
  theme_grey(base_size=15)+scale_fill_discrete(name="Cluster")+
  theme(axis.text.x=element_text(angle=90,vjust=.25,hjust=1))

#Create a blank variable to store each observation's cluster assignment
data$cluster<-NA

#Assign each observation to its cluster
data$cluster[rowSums(is.na(data[,37:82]))==0]<-clust$cluster

#Create labels for the clusters
clustNames<-c("~M4W Hookups","~Kink","~Longer Term","~Anon. Sex","~Gay Male Sex")

#Create a variable reflecting relative cluster score on theme 1 for labeling
fac1order<-order(clustMeans$mean[clustMeans$factor=="1. Companionship"],decreasing=T)

#Relabel clusters based on this order
data$cluster<-mapvalues(data$cluster,fac1order,clustNames[fac1order])

#Reorder factor levels
data$cluster<-factor(data$cluster,levels=clustNames[fac1order])

#Re-generate the cluster mean dataframe
clustMeans2<-data.frame("cluster"=rep(mapvalues(1:5,
                                                fac1order,
                                                clustNames[fac1order]),
                                      times=nrow(faclabels)),
                        "factor"=rep(faclabels$label,each=5),
                        "mean"=as.vector(clust$centers))

#Reorder factor levels
clustMeans2$cluster<-factor(clustMeans2$cluster,levels=clustNames[fac1order])

#Re-generate cluster plot
kMeansPlot2<-qplot(factor,mean,fill=cluster,data=clustMeans2,
                   geom="blank",xlab="Theme",ylab="Mean (Z-scored)")+
  geom_bar(stat="identity",position="dodge",width=.75,color="black")+
  theme_grey(base_size=15)+scale_fill_discrete(name="Cluster")+
  theme(axis.text.x=element_text(angle=90,vjust=.25,hjust=1))

```

### Q3.1 Theme Correlation Network

Plotting the correlation network reveals an interesting polarity in the themes, with themes pertaining to primarily sexual, opportunistic, short-duration relationships tending to co-occur separate from themes pertaining to relationships that are more romantic, committed, and potentially long-term. 

Community detection splits the network in two, with one community containing themes pertaining to gay male sex, anonymous sex, and kinky sex largely belonging to one community and themes pertaining to committed relationships and men pursuing heterosexual relationships with women belonging to a separate community.

It is worth cautioning, though, that the long-term/short-term distinction appears to covary strongly with sexual-orientation, with many of the "shorter-term" themes also relating to gay male relationships (although this sexual orientation and mating strategy do tend to be correlated)

`r cornet2`

### Q3.2 k-Means Cluster Analysis of Themes

A k-means cluster analysis of the ads based on theme scores suggest ads can reasonably be broken into ~5 clusters. Based on average theme scores, these seem to correspond to:  
~M4W Hookups  
~Kink  
~Longer-Term Relationships  
~Anonymous Sex  
~Gay Male Sex

Average standardized theme scores help interpret what these clusters correspond to:  
`r kMeansPlot2`

Here again, it seems that ads seeking long-term, committed, romantic relationships separate out from ads seeing short-term, primarily sexual relationships. It is noteworthy, though, that this does not appear driven entirely by sexual orientation given the emergence of separate M4W Hookups, Anonymous Sex, and Gay Male Sex clusters.

***

# Q4: Are there gender/sexual orientation differences in theme use?

```{r sexDiffsTheme}

###Gender Differences in Theme Scores###


#Create a dataframe to store mean theme scores
sexDiffs<-data.frame("gso"=c("m4m","m4w","w4m","w4w"))

#Calculate mean theme scores
diffMat<-apply(data[,37:82],2,function(x) 
  tapply(scale(x),
         data$gso,
         function(y) 
           mean(y,na.rm=T))[c(1:3,8)])

#Add them to the dataframe and rename
sexDiffs<-cbind(sexDiffs,diffMat)

colnames(sexDiffs)<-c("gso",as.character(faclabels$label))

#Melt the dataframe
sexDiffs<-melt(sexDiffs,id.vars="gso")

#And plot
sexDiffPlot<-qplot(variable,value,fill=gso,data=sexDiffs,
                   geom="blank",xlab="Theme",ylab="Mean (z-scored)")+
  geom_bar(stat="identity",position="dodge",width=.75,color="black")+
  theme_grey(base_size=15)+
  theme(axis.text.x=element_text(angle=90,vjust=.25))+
  scale_fill_discrete(name="Gender/Sex\nOrient.")



##Re-calculating after removing the large number of suspiciously young women...##
#First, create a variable that reflects whether a person reports their age as under 25
#People who don't report or who report ages over 25 are categorized as "doesn't report under 25"
data$u25<-ifelse(data$age>25 |
                   is.na(data$age)==T,
                 "Doesn't Report Under 25",
                 "Reports Under 25")

wAgeDiffs<-data.frame("age"=c("Doesn't Report Under 25","Reports Under 25"))

#Compute theme score differences between women who report being under 25 and women who don't
wAgeDiffs<-cbind(wAgeDiffs,
                 sapply(37:82,function(x)
                   tapply(data[data$gso=="w4m",x],
                          data$u25[data$gso=="w4m"],
                          function(x) mean(x,na.rm=T))))

colnames(wAgeDiffs)<-c("age",as.character(faclabels$label))

#Melt, as before
wAgeDiffs<-melt(wAgeDiffs,id.vars="age")

#Plot differences in theme scores between women who report being under 25 and those who don't
wAgeDiffPlot<-qplot(variable,value,fill=age,data=wAgeDiffs,
                    geom="blank",xlab="Theme",ylab="Mean (z-scored)")+
  geom_bar(stat="identity",position="dodge",width=.75,color="black")+
  theme_grey(base_size=15)+
  theme(axis.text.x=element_text(angle=90,vjust=.25))+
  scale_fill_discrete(name="Age Category")

#Drop all women who report an age 25 or under
datawfix<-data[((data$gso=="w4w" & data$age<=25) |
                  (data$gso=="w4m" & data$age<=25))==F,]

#Create a dataframe to store mean theme scores
sexDiffs2<-data.frame("gso"=c("m4m","m4w","w4m","w4w"))

#calculate mean theme scores
diffMat2<-apply(datawfix[,37:82],2,function(x) tapply(scale(x),datawfix$gso,function(y) mean(y,na.rm=T))[c(1:3,8)])

#Add them to the dataframe and rename
sexDiffs2<-cbind(sexDiffs2,diffMat2)

colnames(sexDiffs2)<-c("gso",as.character(faclabels$label))

#Melt the dataframe
sexDiffs2<-melt(sexDiffs2,id.vars="gso")

#And plot
sexDiffPlot2<-qplot(variable,value,fill=gso,data=sexDiffs2,geom="blank",xlab="Theme",ylab="Mean (z-scored)")+
  geom_bar(stat="identity",position="dodge",width=.75,color="black")+theme_grey(base_size=15)+
  theme(axis.text.x=element_text(angle=90,vjust=.25))+
  scale_fill_discrete(name="Gender/Sex\nOrient.")

```


```{r sexDiffsClusts}

###Clusters by GSO###

#Create a dataframe of GSO frequency by cluster
gsoClust<-as.data.frame(table(data2$gso,data2$cluster))

#Rename variables
colnames(gsoClust)<-c("gso","cluster","count")

#Calculate proportions of each GSO group within cluster
gsoClust$gsoprop<-100*sapply(1:nrow(gsoClust),function(x)
  gsoClust$count[x]/sum(gsoClust$count[gsoClust$gso==gsoClust$gso[x]]))


#Plot GSO as a function of cluster
gsoClustPlot<-qplot(cluster,gsoprop,fill=gso,data=gsoClust,
                    xlab="Cluster",ylab="Proportion of Ads (by Cluster)",geom="blank")+
  geom_bar(stat="identity",position="dodge",color="black")+
  theme_grey(base_size=15)+
  annotate("text",label=paste0("Total =\n",
                               format(tapply(gsoClust$count,
                                             gsoClust$cluster,
                                             sum),big.mark=",")),
           x=1:5,
           y=tapply(gsoClust$gsoprop,
                    gsoClust$cluster,
                    function(x) 10+max(x)))

#Same thing, but plotting clusters within GSO group
gsoClustPlot2<-qplot(gso,gsoprop,fill=cluster,data=gsoClust,
                     xlab="Gender/Sexual Orientation",
                     ylab="Proportion of Ads (by G/SO)",
                     geom="blank")+
  geom_bar(stat="identity",position="dodge",color="black")+
  theme_grey(base_size=15)



#Repeat the analyses above but ommitting suspiciously young women
data3<-datawfix[datawfix$gso %in% c("m4m","m4w","w4m","w4w"),]
data3$gso<-droplevels(data3$gso)

##Breaking down Clusters by GSO##
#Create a dataframe of GSO frequency by cluster
gsoClustWfix<-as.data.frame(table(data3$gso,data3$cluster))

#Rename variables
colnames(gsoClustWfix)<-c("gso","cluster","count")

gsoClustWfix$gsoprop<-100*sapply(1:nrow(gsoClustWfix),function(x)
  gsoClustWfix$count[x]/sum(gsoClustWfix$count[gsoClustWfix$gso==gsoClustWfix$gso[x]]))


#Plot GSO as a function of cluster
gsoClustPlotWfix<-qplot(cluster,gsoprop,fill=gso,data=gsoClustWfix,xlab="Cluster",ylab="Proportion of Ads (by Cluster)",geom="blank")+
  geom_bar(stat="identity",position="dodge",color="black")+theme_grey(base_size=15)+
  annotate("text",label=paste0("Total =\n",format(tapply(gsoClustWfix$count,gsoClustWfix$cluster,sum),big.mark=",")),x=1:5,y=tapply(gsoClustWfix$gsoprop,gsoClustWfix$cluster,function(x) 10+max(x)))

#Same thing, but plotting clusters within GSO group
gsoClustPlot2Wfix<-qplot(gso,gsoprop,fill=cluster,data=gsoClustWfix,xlab="Gender/Sexual Orientation",ylab="Proportion of Ads (by G/SO)",geom="blank")+
  geom_bar(stat="identity",position="dodge",color="black")+theme_grey(base_size=15)
```

Note: all graphs in this section are excluding all women who report being under 25 years of age. There's a suspiciously large number of ads (*n* = `r nrow(data)-nrow(datawfix)`) from women who specifically mention being 25 or younger and these ads differ slightly from ads that don't mention age or don't mention being under 25. For that reason, these ads are excluded here--however, doing so does not substantially change these results.

### Q4.1 Gender Differences in Theme Scores

Plotting average theme score as a function of gender and sexual orientation largely just reveals that gay men separate from the other gender/sexual orientation groups in having higher scores on themes pertaining to gay male sex and anonymous sex.

```{r sexDiffsThemesPlot}

sexDiffsPlot2

```

### Q4.2 Gender Differences in Clusters

Gender and sexual orientation differences in theme use are clearer when looking at the k-means clusters. Here it is clear that the majority of ads in the ~Longer term cluster are coming from w4m or w4w, followed by m4w. Relatively few from from m4m. M4W Hookups is dominated by m4w and w4w, not w4m or m4m. ~Anonymous Sex and Gay Male Sex are dominated by m4m, though more w4m appear in the anonymous sex than m4w (though both are relatively rare).  

```{r sexDiffsClustPlot}

gsoClustPlotWfix

```

Plotting this within gender/sexual orientation category can also clarify the primary emphases of each group:  
```{r sexDiffsClustPlot2}
gsoClustPlot2Wfix
```

Here we see most of the ads for m4m are focusing on short-term relationships as compared to long-term relationships. M4w focus roughly equally on long-term relationships and hookups. W4m and w4w focus overwhelmingly on long-term relationships, though w4w do have some focus on hookups.



